Tickle me BERT: Using laughter to probe pre-trained encoders for dialogue act recognition

### 2019-12-09 reports/ACL2020 Paper/acl2020-paper.tex
Auch, typo in the title
Fix typos

\title{Tickle me BERT: Using laughter to probe pre-trained encoders for dialogue act recoginiton}

@@

Most successful neural approaches also model some notion of context.
We follow previous work that models dialogue act sequences with an RNN over utterances \citep{kalchbrennerRecurrentConvolutionalNeural2013,tranHierarchicalNeuralModel2017,botheContextbasedApproachDialogue2018}.
Our model predicts the most likely tag given the hidden state of the RNN at each position, though other work has shown that DAR benefits from more sophistacted approaches, such as conditional random field \citep{chenDialogueActRecognition2017} or uncertainty propegation \citep{tranPreservingDistributionalInformation2017}.

@@

Recently, neural models trained on large datasets with various unsupervised tasks have found success creating sentence-level and contextual word representations. 
BERT, a multi-layer tranformer, is one such model \citep{devlinBERTPretrainingDeep2018} . 
BERT is pre-trained on two unsupervised tasks: \emph{masked token prediction} and \emph{next sentence prediction}.
In masked token prediction, some percentage of words are randomly replaced with a \texttt{[MASK]} token, and the model is trained to predict the identity of these tokes based on the context sentence.
In next sentence prediction, the model is give two sentences and trained to predict whether the second sentence follows the first in the original text, or if it was randomly chosen from elsewhere in the corpus.
After pre-training, BERT can be applied to a supervised task by adding additional un-trained layers that take the hidden state of one or more of BERT's layers as input.

There is some preivous work applying BERT to dialogue.
\citet{baoPLATOPretrainedDialogue2019,chenSemanticallyConditionedDialog2019a} and both use BERT for dialogue generation tasks.
Similarly \citet{vigComparisonTransferLearningApproaches2019} finds BERT useful for selecting a response from a list of candidate responses in a dialogue.
Finally, \citet{mehriPretrainingMethodsDialog2019} evaluates BERT in various dialogue tasks including DAR, and find that a model incorporating BERT outperforms a baseline model.

@@

\paragraph{Preprocesing}
% - Preprocessing: remove disfluencies, acronyms and speaker tokens in AMI, removing laughter % Bill

@@

The pre-trained model is more accurate than the randomly initialized model by several percentage points on both DA corpora,
suggesting that BERT's extensive pre-training does provide some useful information for recoginizing different dialogue acts (Table~\ref{table:exp2}).
This performance boost is much more pronounced in the macro-averaged F1 score,
which is explained by the fact that at the tag level, pre-training has a larger impact on less frequent tags.
For a disaggregeated view, see Figure \ref{fig:f1-by-da} in Appendix~\ref{sec:suppl}.

>>>>

\title{Tickle me BERT: Using laughter to probe pre-trained encoders for dialogue act recognition}

@@

Most successful neural approaches also model some notion of context.
We follow previous work that models dialogue act sequences with an RNN over utterances \citep{kalchbrennerRecurrentConvolutionalNeural2013,tranHierarchicalNeuralModel2017,botheContextbasedApproachDialogue2018}.
Our model predicts the most likely tag given the hidden state of the RNN at each position, though other work has shown that DAR benefits from more sophisticated approaches, such as conditional random field \citep{chenDialogueActRecognition2017} or uncertainty propagation \citep{tranPreservingDistributionalInformation2017}.

@@

Recently, neural models trained on large datasets with various unsupervised tasks have found success creating sentence-level and contextual word representations. 
BERT, a multi-layer transformer, is one such model \citep{devlinBERTPretrainingDeep2018} . 
BERT is pre-trained on two unsupervised tasks: \emph{masked token prediction} and \emph{next sentence prediction}.
In masked token prediction, some percentage of words are randomly replaced with a \texttt{[MASK]} token, and the model is trained to predict the identity of these tokes based on the context sentence.
In next sentence prediction, the model is give two sentences and trained to predict whether the second sentence follows the first in the original text, or if it was randomly chosen from elsewhere in the corpus.
After pre-training, BERT can be applied to a supervised task by adding additional un-trained layers that take the hidden state of one or more of BERT's layers as input.

There is some previous work applying BERT to dialogue.
\citet{baoPLATOPretrainedDialogue2019,chenSemanticallyConditionedDialog2019a} and both use BERT for dialogue generation tasks.
Similarly \citet{vigComparisonTransferLearningApproaches2019} finds BERT useful for selecting a response from a list of candidate responses in a dialogue.
Finally, \citet{mehriPretrainingMethodsDialog2019} evaluates BERT in various dialogue tasks including DAR, and find that a model incorporating BERT outperforms a baseline model.

@@

\paragraph{Preprocessing}
% - Preprocessing: remove disfluencies, acronyms and speaker tokens in AMI, removing laughter % Bill

@@

The pre-trained model is more accurate than the randomly initialized model by several percentage points on both DA corpora,
suggesting that BERT's extensive pre-training does provide some useful information for recoginizing different dialogue acts (Table~\ref{table:exp2}).
This performance boost is much more pronounced in the macro-averaged F1 score,
which is explained by the fact that at the tag level, pre-training has a larger impact on less frequent tags.
For a disaggregated view, see Figure \ref{fig:f1-by-da} in Appendix~\ref{sec:suppl}.
